THESIS PROJECT PROPOSAL

### 2019-11-16 project_ashish/paper.tex
Update paper.tex

The event reconstruction is designed to capture the distinguishing features of the signal topology.
In the channels which are the focus of this project we require that there be at least two leptons of electron or muon type, however also jets need to be identified as shown in the figure.
The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{ref:cmssw} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
A new data structure at this level defines new datasets stored in computing centers around the world which are available to students and scientists at all research institutions.

>>>>

The event reconstruction is designed to capture the distinguishing features of the signal topology.
In the channels which are the focus of this project we require that there be at least two leptons of electron or muon type, however also jets need to be identified as shown in the figure.
The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:2006nff} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
A new data structure at this level defines new datasets stored in computing centers around the world which are available to students and scientists at all research institutions.
